### 2018-08-09 TeX/organigram2.tex
changed a lot

\documentclass{article}
%\usepackage{graphicx} % includegraphics
\usepackage{tikz}
\usetikzlibrary{trees, arrows, shapes.geometric} % TikZ libraries
\usepackage{lscape}

@@

% tree styles (defined by template)
\tikzstyle{every node}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
% self defined
\tikzstyle{io}=[rectangle, rounded corners, minimum width = 2cm, minimum height = 1cm, text centered, draw = black, fill = blue!10]
\tikzstyle{main}=[rectangle, rounded corners, minimum width = 3cm, minimum height = 1cm, text centered, draw = black, fill = red!30]
\tikzstyle{ids}=[diamond, minimum width = 3cm, minimum height = 1cm, text centered, draw = black, fill = green!30]
\tikzstyle{res}=[rectangle, rounded corners, minimum width = 2cm, minimum height = 1cm, text centered, draw = black, fill = blue!30]

%arrows
\tikzstyle{arrow} = [thick, ->, > = stealth]

@@

\draw[thick] (current page.south west) rectangle (current page.north east); % debuging

%% chemicals
% id nodes
\node (cas) [ids, below of=io, yshift = -4cm] {CAS};
% main nodes
\node (epa) [main, right of=cas, yshift=1cm, xshift=3cm] {EPA ectox tests}
	child { node { qu\_epa.R} };
\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=3cm] {Chemical scripts ch}
	child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
	child { node { Pesticide Action Network - \textbf{ch\_pp.R} }}
	child { node { PhysProp - \textbf{ch\_pp.R} }}
	child { node { PubChem - \textbf{qu\_pubchem.R} }
		child { node { Variable - InchiKey }} };
% result nodes
\node (toxres) [res, right of=cas, yshift=0cm, xshift=7cm] {ETOX Test Results}; % result
%\includegraphics{/home/andreas/Documents/Projects/etox-base/data/pubchemlogo2017.png};

@@

%% organisms
% id nodes
\node (taxon) [ids, below of=cas, yshift=-9cm, align = center] {Taxon}; % \\ {(Genus or Species)}}; % escape brackets usin curly brackets
% main nodes
\node (taxonquery) [main, right of=taxon, xshift=3cm, yshift=0cm] {Taxonomic data};
\node (habitat) [main, right of=taxon, xshift=3cm, yshift=1.5cm] {Habitat data}
	child { node { WORMS data base - \textbf{tx\_worms.R} }
		child { node { Family }}
		child { node { Species }} }
	child [dashed] { node { Freshwaterecology.info data }} ;
\node (region) [main, right of = taxon, xshift=3cm, yshift=-1.5cm] {Regional data};
% result nodes
\node (taxres) [res, right of=taxon, xshift=7cm] {Taxon and Habitat Result}; % result

%% final result
\node (testres) [res] at (15,-5) {Final result};

%%% arrows %%%
\draw [arrow] (io) -- (cas);
\draw [->] (cas) -- node[anchor = east] {receive} (chemscr);
\draw [->, dashed] (cas) -- node[anchor = south] {receive} (epa);
\draw [->] (epa) -- (toxres);
\draw [->] (chemscr) -- (toxres);
\draw [->] (toxres) .. controls (5,-6) and (1,-4) .. (taxon);
\draw [->] (taxon) -- (habitat);
\draw [->] (taxon) -- (region);
\draw [->] (taxon) -- (taxonquery);
\draw [->] (habitat) -- (taxres);
\draw [->] (taxonquery) -- (taxres);
\draw [->] (region) -- (taxres);
\draw [->] (toxres) -- (testres);
\draw [->] (taxres) -- (testres);
\draw [->, dashed] (testres) -- (20,-5);

@@

\clearpage

@@

%% entities
\node [res] (clean) at (-5,5) {Cleaning};
\node (filter) [res, right of = clean, xshift = 3cm] {Filter};
\node (agg1) [res, right of = filter, xshift = 3cm] {Aggregation 1};
\node (agg2) [res, right of = agg1, xshift = 3cm] {Aggregation 2};

>>>>

\documentclass{article}
%\usepackage{graphicx} % includegraphics
%% packages
\usepackage{tikz}
\usetikzlibrary{trees, arrows, shapes.geometric} % TikZ libraries
%\usetikzlibrary{backgrounds}
\usepackage{lscape}

%% layers
\pgfdeclarelayer{bg1}    % declare background layer
\pgfdeclarelayer{bg2}
\pgfsetlayers{bg2,bg1,main}  % set the order of the layers (main is the standard layer)

@@

% tree styles (defined by template)
\tikzstyle{every node}=[draw=black,thick,anchor=west]
%\tikzstyle{selected}=[draw=red,fill=red!30]
%\tikzstyle{optional}=[dashed,fill=gray!50]
% self defined
\tikzstyle{io}=[rectangle, minimum width = 4cm, minimum height = 1cm, text centered, draw = black, fill = blue!10]
\tikzstyle{main}=[rectangle, rounded corners, minimum width = 3cm, minimum height = 1cm, text centered, draw = black, fill = purple!30]
\tikzstyle{ids}=[diamond, minimum width = 3cm, minimum height = 1cm, text centered, draw = black, fill = green!30]
\tikzstyle{res}=[rectangle, rounded corners, minimum width = 2cm, minimum height = 1cm, text centered, draw = black, fill = blue!30]
\tikzstyle{resvariables}=[rectangle, minimum width = 2cm, minimum height = 1cm, text centered, draw = black]
\tikzstyle{steps} = [rectangle, minimum width = 1cm, text centered, fill = yellow]

%arrows
\tikzstyle{arrow} = [->, > = stealth, draw = black, color = yellow!80, line width = 6pt]
% TODO double colored arrows - don't know how it works
\iffalse
\tikzset{
	darrow/.style args={#1 colored by #2 and #3}{
		-stealth,line width=#1,#2, % first arrow
		postaction={draw,-stealth,#3,line width=(#1)/3,
			shorten <=(#1)/3,shorten >=2*(#1)/3}, % second arrow
	}
}
\fi

@@

% \draw[thick] (current page.south west) rectangle (current page.north east); % debuging

%% chemicals
% id nodes
\node (cas) [ids, below of=io, yshift = -4cm] {CAS};
% main nodes
\node (chemprop) [main, dashed, right of=cas, xshift=4.5cm, yshift=3cm] {CHEMPROP};
\node (epa) [main, right of=cas, yshift=1cm, xshift=4.5cm] {EPA ectox tests}
	child { node { qu\_epa.R} };
\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=4.5cm] {Chemical scripts ch}
	child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
	child { node { Pesticide Action Network - \textbf{ch\_pp.R} }}
	child { node { PhysProp - \textbf{ch\_pp.R} }}
	child { node { PubChem - \textbf{qu\_pubchem.R} }};
% result nodes
\node (toxres) [resvariables, right of=cas, yshift=0cm, xshift=16cm, align = left] {Results\\Test results\\Substance type:\\pesticides, metals, etc.}; % result
%\includegraphics{/home/andreas/Documents/Projects/etox-base/data/pubchemlogo2017.png};

@@

%% organisms
% id nodes
\node (taxon) [ids, below of=cas, yshift=-9cm, align = center] {Taxon}; % \\ {(Genus or Species)}}; % escape brackets usin curly brackets
% main nodes
\node (taxonquery) [main, right of=taxon, xshift=4.5cm, yshift=3cm] {Taxonomic data};
\node (habitat) [main, right of=taxon, xshift=4.5cm, yshift=1cm] {Habitat data}
	child { node { WORMS data base - \textbf{tx\_worms.R} }}
	child { node { Manual Search - \textbf{ha\_manual.R} }};
\node (region) [main, right of = taxon, xshift=4.5cm, yshift=-2cm] {Regional data}
	child { node { GBIF - \textbf{qu\_gbif.R} }};
% result nodes
\node (taxres) [resvariables, right of=taxon, xshift=17cm, align = left] {Results:\\Validation of taxonomic ranks\\Habitat information\\Marine, Bracksih, Freshwater, Terrestrial, Parasites\\Occurrence}; % result

%% final result
\node (testres) [res] at (16,-5) {Final result}
	child { node { re\_merge.R} };
\iffalse
node[anchor = south]
node[anchor = east]
\fi

%%% arrows %%%
\begin{pgfonlayer}{bg1}
\draw [arrow, black] (io) -- (cas);
\draw [arrow, dashed] (cas) -- (chemprop);
\draw [arrow] (cas) -- (chemscr);
\draw [arrow] (cas) -- (epa);
\draw [arrow] (epa) -- (toxres);
\draw [arrow] (chemscr) -- (toxres);

%\begin{scope}[on background layer]
\begin{pgfonlayer}{bg2}
	\draw [arrow, black] (epa) .. controls (-2,-4) and (1,-4) .. (taxon);
\end{pgfonlayer}
%\end{scope}

\draw [arrow] (taxon) -- (habitat);
\draw [arrow] (taxon) -- (region);
\draw [arrow] (taxon) -- (taxonquery);
\draw [arrow] (habitat) -- (taxres);
\draw [arrow] (taxonquery) -- (taxres);
\draw [arrow] (region) -- (taxres);
\draw [arrow] (toxres) -- (testres);
\draw [arrow] (taxres) -- (testres);

\draw [arrow, dashed] (testres) -- (20,-5);
\end{pgfonlayer}

@@

%\clearpage

@@

%% entities
\node (clean) [res] at (-5,5) {Cleaning}
	child { node { re\_clean.R} };
\node (filter) [res, right of = clean, xshift = 3cm] {Filter}
	child { node { re\_filter.R} };
\node (plot) [res, right of = filter, xshift = 3cm] {Plots}
	child { node { re\_plot.R} };
\node (agg1) [res, right of = plot, xshift = 3cm] {Aggregation};

\node (write) [io, right of = agg1, xshift = 3cm, yshift = -5cm] {Write tables to data base};

%% cleaning and filter steps
\node (solub) [steps, below of = clean, yshift = -2cm] {Solubility check};
\node (substtype) [steps, below of = solub, yshift = -2cm] {Substance-type: F, AI, U, T};

\node (habitat) [steps, right of = solub, xshift = 7cm] {Habitat: Marine, Brackish, Freshwater, Terrestrial};
\node (region) [steps, right of = solub, xshift = 7cm, yshift = -2cm] {Regions: Americas, Africa, Freshwater, Terrestrial};
\node (duration) [steps, right of = solub, xshift = 7cm, yshift = -4cm] {Tests between 22 and 338h};
\node (taxagroups) [steps, right of = solub, xshift = 7cm, yshift = -6cm] {};

\node (agg1) [steps, right of = solub, xshift = 7cm, yshift = -6cm] {by casnr, taxon and duration};
